\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T20:21:43+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they lead to different probabilities on the
data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant, from this perspective.

@@

Third, \emph{the evidence $\p(D \| M_{i})$ of a model automatically takes
  care of its complexity}. This happens because the probability over the
data space is normalized. If $M_{2}$ has a typical-data volume larger than
$M_{1}$'s, then it must also assign lower probability to each volume
element in that volume, to ensure normalization. As a result, if the
observed data $D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1}) > \pf(D^{*} \| M_{2})$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the observed data are for each model and each
model's power. This is the so-called automatic Ockham razor of Bayes's
theorem, extensively explained by MacKay
\citey{mackay1992}[also][\sect~28.1]{mackay1995_r2003}. And this is the
reason why we are personally satisfied with simply comparing the evidence
for any two models.

In our calculations, however, we are using a zeroth-order Laplace
approximation for calculating the evidence in \sect~4. A first-order
approximation (containing the width of the distribution, influenced by the
typical-set volume above) would correct for the model's power. We believe
that the correction would nevertheless be the same in the calculation based
on the larger population, \eqns~(11), and on the sample, \eqns~(12),
because the data space is the same in both. Hence the difference in the two
approaches -- our main message -- should persist. But it would be better to
check this.

@@

The question, in summary, is what exactly is being compared, whether
families (and what their accompanying distributions are) or single
distributions. The literature is not at all clear. But, in either case, our
calculations show that the approaches based on a population and a sample
thereof can lead to different conclusions -- in accordance with the
non-preservation of sufficiency under sampling -- and they provide a way to
bypass this problem.

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations;
Appendix~C explains where the differences appear. Also, it is important to
know whether we are calculating the frequency of past results, or the
probability for a new result, or the most probable frequency of future
results. These three quantities are very different when the ratio
$\frac{\text{\# samples}}{\text{data-space dimension}}$ is high, and they are
to be used in different ways.

So these are not philosophical matters, it's a matter of understanding what
we are doing and stating it clearly in our work. % Unfortunately the
% neuroscience literature is very unclear on such matters.
There's also another important reason. We are generally concerned for
master's and PhD students, who often learn concepts and methods through
actual research, perusing works like the present one. Young researchers too
often end up learning incorrect or confused ideas, gathered from unclear
literature. They trust it because it's peer-reviewed. Sometimes the result,
quoting Feynman \citey{feynman1985_r1989}, is that \enquote{they don't
  learn by understanding; they learn by some other way -- by rote, or
  something. Their knowledge is so fragile!}. We owe them clarity,
precision, honesty, and at least a glimpse of the bigger picture.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T21:23:04+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they lead to different probabilities on the
data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant, from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those
\citep[\eg][]{copasetal1979,lindleyetal1982} who find such definitions
ultimately arbitrary. Many such distributions lead, moreover, to
mathematical singularities.

@@

Third, \emph{the evidence $\p(D \| M_{i})$ for a model automatically takes
  care of its complexity}. This happens because the probability over the
data space is normalized. If $M_{2}$ has a typical-data volume larger than
$M_{1}$'s, then it must also assign lower probability to each volume
element therein, to ensure normalization. As a result, if the observed data
$D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1}) > \pf(D^{*} \| M_{2})$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the observed data are for each model and each
model's power. This is the so-called automatic Ockham razor of Bayes's
theorem, extensively explained by MacKay
\citey{mackay1992}[also][\sect~28.1]{mackay1995_r2003}. And this is the
reason why we are personally satisfied with simply comparing the evidence
for any two models.

In our calculations, however, we are using a zeroth-order Laplace
approximation for calculating the evidence in \sect~4. A first-order
approximation (containing the width of the distribution, influenced by the
typical-set volume above) would correct for the model's power. We believe
that the correction would nevertheless be the same in the calculations
based on the larger population, \eqns~(11), and on the sample, \eqns~(12).
Hence the difference in the two approaches -- our main message -- should
persist. But it would be better to check this.

@@

The question, in summary, is what exactly is being compared, whether
families (and what their accompanying distributions are) or single
distributions. The literature is unclear and contradictory on this. But, in
either case, our calculations show that the approaches based on a
population and a sample thereof can lead to different conclusions -- in
accordance with the non-preservation of sufficiency under sampling -- and
they provide a way to bypass this problem.

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways.

These are therefore not philosophical matters. It's a matter of
understanding what we are doing and stating it clearly in our
work. % Unfortunately the
% neuroscience literature is very unclear on such matters.
There's also another important reason. We are generally concerned for
master's and PhD students, who often learn concepts and methods through
actual research, perusing works like the present one. Young researchers too
often end up learning incorrect or confused ideas, gathered from unclear
literature. % They trust it because it's peer-reviewed.
Sometimes the result, quoting Feynman \citey{feynman1985_r1989}, is that
\enquote{they don't learn by understanding; they learn by some other way --
  by rote, or something. Their knowledge is so fragile!}. We owe them
clarity, precision, honesty, and a glimpse of the bigger picture.
